Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-15 analysis/paper/paper.Rmd
add figures for parameters

>>>>

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_f1)) + 
  scale_colour_grey() +
  ggtitle("Code")

b <- plot(parameters(m_f2)) + 
  scale_colour_grey() +
   theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    ) +
  ggtitle("Data")

p <- a + b
p <- p +
  plot_annotation(tag_levels = "A") &
  theme(text = element_text("Arial"))

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
```

```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_g1), show_lables = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")

b <- plot(parameters(m_g2), show_lables = TRUE) + 
  scale_colour_grey() +
   theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    ) +
  ggtitle("Data")

p <- a + b
p <- p +
  plot_annotation(tag_levels = "A") &
  theme(text = element_text("Arial"))

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
```

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_h1), show_lables = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")

b <- plot(parameters(m_h2), show_lables = TRUE) + 
  scale_colour_grey() +
   theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    ) +
  ggtitle("Data")

p <- a + b
p <- p +
  plot_annotation(tag_levels = "A") &
  theme(text = element_text("Arial"))

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
```
